%----------HEADING-----------------
\begin{center}
    \textbf{\LARGE Divyank Gupta} \\ \vspace{0.5pt}
    Mumbai, India \enspace \rule{0.75ex}{0.75ex} \enspace \href{mailto:divyank.gupta1000@gmail.com}{divyank.gupta1000@gmail.com} \enspace \rule{0.75ex}{0.75ex} \enspace +91 8879868281 \\ LinkedIn: \href{https://linkedin.com/in/divyaankkk}{linkedin.com/in/divyaankkk} \enspace \rule{0.75ex}{0.75ex} \enspace GitHub: \href{https://github.com/divyaankkk}{github.com/divyaankkk}

\end{center}
    
%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStartNoBullet
\resumeSubheading
{Narsee Monjee Institute of Management Studies, MPSTME, Mumbai}{June 2025}
{Master of Business Administration (Major: Business Intelligence \& Analytics, Minor: Finance)}{GPA: 3.47/4}
\resumeSubheading
{Narsee Monjee Institute of Management Studies, MPSTME, Mumbai}{June 2025}
{Bachelor of Technology in Computer Science}{GPA: 3.47/4}
\resumeSubHeadingListEndNoBullet    

%-----------SKILLS-----------------
\section{Skills}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}
  \textbf{Cloud Computing:} Google Cloud, AWS          & Financial Analysis \& Capital Markets \\
  \textbf{Data Analytics:} Python, PowerBI, SAS, SPSS  & Quantitative Techniques \\
  \textbf{Databases:} SQL, Google Cloud Storage, Amazon S3 & Strategic Planning \\
  \textbf{Automation:} Power Apps, Azure DevOps, Git, IoT  & Microsoft Office: Word, Excel, PowerPoint \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStartNoBullet

\resumeSubheading
{SBI Funds Management Ltd}{Sep 2025 -- Till Date}
{Digital Product Manager}{Mumbai, India}
\resumeItemListStart
\resumeItemWithoutTitle{Managing end-to-end product lifecycle for Mutual Fund investments across B2C and B2B platforms and core banking systems used by 22,000+ branches, building for a 10+ crore user base.}
\resumeItemWithoutTitle{Implementing core product KPIs including transaction success rate and AUM growth, leveraging funnel analytics and customer segmentation to recommend targeted strategies and investment offerings.}
\resumeItemWithoutTitle{Partnering with executive stakeholders and cross-functional teams including Business, Development, Design, QA, and Analytics, translating user insights to refine product experience.}
\resumeItemListEnd

\resumeSubheading
{Shoppers Stop Limited}{May 2024 -- Sep 2024}
{Data Science Intern}{Mumbai, India}
\resumeItemListStart
\resumeItemWithoutTitle{Facilitated enterprise-wide cloud database and ML analytical models migration for market analysis and streamlined insights, achieving cost savings in crores (Rs.) and enhancing data efficiency.}
\resumeItemWithoutTitle{Developed 40+ reports with 1400+ KPIs; advanced customer engagement through Gen AI initiatives, exploring chatbots and virtual try-on technologies.}
\resumeItemListEnd

\resumeSubheading
{Reliance Industries Limited}{Dec 2023 -- Jan 2024}
{Software Development Intern}{Mumbai, India}
\resumeItemListStart
\resumeItemWithoutTitle{Collaborated on the Ministry of Petroleum and Natural Gas (MOPNG) Report for the Refining \& Marketing department, conducting financial and operational analysis using multi-currency datasets and business metrics.}
\resumeItemWithoutTitle{Leveraged data from Azure-based data warehouses for insights on material, financial, and geographic trends.}
\resumeItemListEnd

\resumeSubheading
{Being Ambitious}{May 2023 -- Jul 2023}
{Web Development Intern}{Remote}
\resumeItemListStart
\resumeItemWithoutTitle{Designed and developed wireframes and webpages, coordinating with cross-functional teams to build and deploy a responsive full-stack Café Recommendation platform leveraging Mood API.}
\resumeItemWithoutTitle{Integrated themes, plugins, UI/UX prototyping, and cross-browser testing ensuring alignment with shareholders' requirements.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubItem{Project Ishaare -- Indian Sign Language Recognition System}
{Developed a Python-based web software for Indian Sign Language Recognition with Hindi Translation. Implemented a comprehensive pipeline for data collection, hand gesture analysis, and model training using Random Forest and CNN classifiers, achieving 98\% accuracy.}

\resumeSubItem{Chronic Kidney Disease Detection}
{Developed tree-based ensemble ML models (Random Forest, Gradient Boosting, AdaBoost) on a pre-processed 24-feature dataset, achieving 78--99\% accuracy.}

\resumeSubItem{Real-Time Face Recognition System}
{Built a real-time face detection and localization system using CNN with VGG16, leveraging TensorFlow for model training and bounding box regression, alongside advanced data augmentation techniques.}

\resumeSubItem{Equity Analysis of the Indian Cement Industry}
{Analysed financial statements of 6 cement sector companies, computed 20+ financial ratios, conducted comprehensive peer analysis, and applied DuPont's 5-factor analysis.}

\resumeSubItem{5Q Assessment Manual (From Effectiveness to Completeness)}
{Designed a 4-degree, 18-factor self-assessment manual to measure Physical Quotient, EQ, Creativity Quotient, IQ, and SQ, applying Linear Programming models.}

\resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------------
\section{Certifications \& Publications}
\resumeSubHeadingListStart

\resumeSubItem{Google}
{Data Analytics, Generative AI, and Big Data}

\resumeSubItem{Project Management Institute (PMI) \& Microsoft}
{Business Analysis}

\resumeSubItem{Bloomberg}
{Finance Fundamentals and Market Concepts}

\resumeSubItem{Publication}
{Machine Learning Advancements in Identification of Insider Trading -- \textit{IJSDR Vol. 7, Nov 2022}}

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS & INTERESTS-----------------
\section{Achievements \& Interests}
\resumeSubHeadingListStart
\resumeSubheadingWithoutTitle{House Captain and Member of School Council}{}
\resumeSubheadingWithoutTitle{Member of Organising Committee in Food Donation and Tree Plantation Drives}{}
\resumeSubheadingWithoutTitle{Directed and Performed for a Short Film Festival on Swachh Bharat Abhiyan}{}
\resumeSubheadingWithoutTitle{\textbf{Interests:} Swimming, Table Tennis, Football, Skating, Piano, Photography}{}
\resumeSubHeadingListEnd
